Mungbean Powdery Mildew Spray Timing

### 2019-10-30 Cluster Timing/MB_PM_data.Rmd
Rearrange first step and spellcheck

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(skimr)
mb <- read_csv("data/slim-mungbean-powdery_mildew.csv")
```

@@

```{r mutate-filter}
mb <-
  mb %>%
  mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
  mutate_at(vars(starts_with("fungicide_application_")), dmy) %>%
  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
  mutate(fungicide_timing_2 = fungicide_application_2 - first_sign_disease) %>%
  select(-c(fungicide_application_3:fungicide_application_7)) %>%
  filter(!is.na(grain_yield.t.ha.))
```

@@

Note that the cluster for the second spray "reccomended" is from Day 13, not Day 14.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(skimr)
mb <- read_csv("slim-mungbean-powdery_mildew.csv")
```

@@

```{r mutate-filter}
mb <-
  mb %>%
  select(-c(fungicide_application_3:fungicide_application_7)) %>%
  mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
  mutate_at(vars(starts_with("fungicide_application_")), dmy) %>%
  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
  mutate(fungicide_timing_2 = fungicide_application_2 - first_sign_disease) %>%
  filter(!is.na(grain_yield.t.ha.))
```

@@

Note that the cluster for the second spray "recommended" is from Day 13, not Day 14.
